Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-25 xrb/submit/paper.tex
Make opening sentence of paragraph comparing to Yuri's papers clearer

\added{The computational expense of the problem necessitated several approximations
to make this set of simulations \citep{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal, Cavecchi2019}
tractable. The first was the assumption of vertical hydrostatic equilibrium, which
allowed them to filter out vertically propagating sound waves that would otherwise
have limited the timestep. This enabled them to reach the simulation times (on the
order of seconds) needed to capture the rise of the burst, but they could not model
vortical fluid motions driven by effects such as turbulence and convection. These can
facilitate mixing and help to accelerate the propagation of the flame front. They also
included only the triple-$\alpha$ process in their implementation of nuclear burning,
and use a fixed, constant opacity across the entire domain for each simulation run (although
they explore the dependence of the flame propagation speed on this opacity value).
Our simulations relax the assumption of vertical hydrostatic equilibrium, and implement
a more complete set of nuclear reactions and opacities. However, as discussed later, this
comes at the expense of a different set of approximations.}

>>>>

\added{The computational expense of the problem necessitated several approximations
to make the simulations of \citet{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal}
and \citet{Cavecchi2019} tractable. The first was the assumption of vertical hydrostatic equilibrium,
which allowed them to filter out vertically propagating sound waves that would otherwise
have limited the timestep. This enabled them to reach the simulation times (on the
order of seconds) needed to capture the rise of the burst, but they could not model
vortical fluid motions driven by effects such as turbulence and convection. These can
facilitate mixing and help to accelerate the propagation of the flame front. They also
included only the triple-$\alpha$ process in their implementation of nuclear burning,
and use a fixed, constant opacity across the entire domain for each simulation run (although
they explore the dependence of the flame propagation speed on this opacity value).
Our simulations relax the assumption of vertical hydrostatic equilibrium, and implement
a more complete set of nuclear reactions and opacities. However, as discussed later, this
comes at the expense of a different set of approximations.}
